Abstract Binding Trees

### 2015-10-25 paper.tex
further fixes to refinements
typos

Abts are identified up to $\alpha$-equivalence. Let $\FS{M}$
be the collection of symbols free in $M$, and let $\FV{M}$ be the collection of
variables free $\pi_\Operators$ to operators in $M$. %% TODO: actually define these

@@

Suppose we have defined encoded a fragment of type theory as well:
\[
  \begin{array}{l}
    \IsOperator{\Upsilon}{\top}{
      \MkArity{}{\SortType}
    }\\
    \IsOperator{\Upsilon}{\bot}{
      \MkArity{}{\SortType}
    }\\
    \IsOperator{\Upsilon}{\OpBool}{
      \MkArity{}{\SortType}
    }\\
    \IsOperator{\Upsilon}{\OpSo}{
      \MkArity{
        \MkValence{}{}{\SortExp}
      }{\SortType}
    }\\
    \IsOperator{\Upsilon}{\OpPi}{
      \MkArity{
        \MkValence{}{}{\SortType},
        \MkValence{}{\SortExp}{\SortType}
      }{\SortType}
    }\\
    \IsOperator{\Upsilon}{\OpSg}{
      \MkArity{
        \MkValence{}{}{\SortType},
        \MkValence{}{\SortExp}{\SortType}
      }{\SortType}
    }\\
  \end{array}
\]

@@

The remainder of the definition of refinement proceeds by induction on sorts
and operators. For the sake of this example, we will just stipulate that
anything of sort $\SortExp$ or $\SortType$ is grammatical:

\begin{align*}
  \infer{
    \IsWf{\Omega}{\Upsilon}{\Gamma}{A}{\SortType}
  }{
  }\qquad
  \infer{
    \IsWf{\Omega}{\Upsilon}{\Gamma}{M}{\SortExp}
  }{
  }
\end{align*}

The refinements for parametric judgment and sequents simply delegate to their
subterms:
\begin{gather*}
  \infer{
    \IsWf{\Omega}{\Upsilon}{\Gamma}{
      \App{\OpNabla{\vec{s}}}{
        \MkBTm{\vec{u}}{}{J}
      }
    }{\SortJdg}
  }{
    \IsWf{\Omega}{\Upsilon,\vec{u}:\vec{s}}{\Gamma}{J}{\SortJdg}
  }\\[6pt]
  \infer{
    \IsWf{\Omega}{\Upsilon}{\Gamma}{
      H\gg A
    }{\SortJdg}
  }{
    \IsWf{\Omega}{\Upsilon}{\Gamma}{H}{\SortTele} &
    \IsWf{\Omega}{\Upsilon}{\Gamma}{A}{\SortType}
  }
\end{gather*}

>>>>

Abts are identified up to $\alpha$-equivalence. Let $\FS{M}$ be the collection
of symbols free in $M$, and let $\FV{M}$ be the collection of variables free in
$M$. %% TODO: actually define these

@@

Suppose we have encoded a fragment of type theory as well:
\[
  \begin{array}{l}
    \IsOperator{\Upsilon}{\top}{
      \MkArity{}{\SortType}
    }\\
    \IsOperator{\Upsilon}{\bot}{
      \MkArity{}{\SortType}
    }\\
    \IsOperator{\Upsilon}{\OpBool}{
      \MkArity{}{\SortType}
    }\\
    \IsOperator{\Upsilon}{\OpSo}{
      \MkArity{
        \MkValence{}{}{\SortExp}
      }{\SortType}
    }\\
    \IsOperator{\Upsilon}{\OpPi}{
      \MkArity{
        \MkValence{}{}{\SortType},
        \MkValence{}{\SortExp}{\SortType}
      }{\SortType}
    }\\
    \IsOperator{\Upsilon}{\OpSg}{
      \MkArity{
        \MkValence{}{}{\SortType},
        \MkValence{}{\SortExp}{\SortType}
      }{\SortType}
    }\\
  \end{array}
\]

@@

The remainder of the definition of refinement proceeds by induction on sorts
and operators. For the sake of this example, we will just stipulate that
anything of sort $\SortExp$ or $\SortType$ is grammatical if its subterms are
grammatical:

\[
  \infer[
    \text{for $\Member{s}{\MkSet{\SortExp,\SortType}}$}
  ]{
    \IsWf{\Omega}{\Upsilon}{\Gamma}{
      \App{\vartheta}{E_0,\dots,E_n}
    }{s}
  }{
    \begin{array}{l}
      \IsOperator{\Upsilon}{\vartheta}{
        \MkArity{
          v_0,\dots,v_n
        }{s}
      }\\
      \HypJ{
        \IsWf{\Omega}{\Upsilon}{\Gamma}{E_i}{v_i}
      }{
        \Leq{i}{n}
      }
    \end{array}
  }
\]

The refinements for parametric judgment and sequents simply delegate to their
subterms as well:
\begin{gather*}
  \infer{
    \IsWf{\Omega}{\Upsilon}{\Gamma}{
      \App{\OpNabla{\vec{s}}}{
        \MkBTm{\vec{u}}{}{J}
      }
    }{\SortJdg}
  }{
    \IsWf{\Omega}{\Upsilon,\vec{u}:\vec{s}}{\Gamma}{J}{\SortJdg}
  }\\[6pt]
  \infer{
    \IsWf{\Omega}{\Upsilon}{\Gamma}{
      H\gg A
    }{\SortJdg}
  }{
    \IsWf{\Omega}{\Upsilon}{\Gamma}{H}{\SortTele} &
    \IsWf{\Omega}{\Upsilon}{\Gamma}{A}{\SortType}
  }
\end{gather*}
